---
title: "K2 targets"
author: "J. Dotson"
date: "12/5/2019"
output: html_document
---

For future use, reading in the full GO target list and manipulating it...  (Target list from the keplerscience.arc.nasa.gov site)

**Note, as of 12/26/1019, this doesn't include the engineering campaign...  :(

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

require(ggplot2)
require(dplyr)
require(knitr)
require(readr)
require(ggridges)
require(gridExtra)
require(summarytools)
require(truncnorm)
require(sjmisc)
require(snakecase)
require(stringr)

require(progress)


knitr::opts_knit$set(root.dir = '../.')
myecho = TRUE
```

Input

```{r input}
k2 <- read_csv("k2-lists/GO_all_campaigns_to_date.csv")
```

simplify column headings
```{r}
mycols <- c("epic", "RA", "Dec", "mag","Investigation_id", "campaign")
colnames(k2) <- mycols
```



let's get rid of the custom masks...

```{r }
k2_real_targets <- k2 %>% filter(!is.na(RA))

#Making sure the Decs are all there
jj <- which(is.na(k2_real_targets$Dec))
```



```{r}

thesecols <- c("RA", "Dec")
k2_coords <- k2_real_targets %>% select(thesecols)

write_csv(k2_coords, "k2-lists/k2_unique_targets.csv")

```

Write this out in chunks for use with the TESS visibility tool

```{r}
num_sources <- nrow(k2_coords)
j <- 1
group_size <- 10000
num_steps <- ceiling(num_sources / group_size)

filename_base <- "partial_k2_list-"

for (i in 1:num_steps){
  k <- i * group_size
  if (k > num_sources){
    k <- num_sources
  }
  temp <- k2_coords[j:k,]
  thisfile <- paste("k2-lists/smaller-k2-lists/",filename_base,i,".csv",sep="")
  write_csv(temp,thisfile,col_names=FALSE)
  j <- k + 1
}


```

I then manually upload these lists into the Web TESS Viewer tool.  The results are in overlaplists/smaller-wtv-results.  Now need to match these back up with their EPIC ids.  This will create a new all unique targets overlap list with the correct pointings for Cycle 2 and the anticipated ones for Cycle 3.

Read these wtv results in, concatenate them.

```{r}

for (i in 1:num_steps){
  thisfile <- paste("overlaplists/smaller-wtv-results/wtv-partial_k2_list-",i,".csv",sep="")
  temp <- read_csv(thisfile,skip=44)
  if (i == 1) {
    wtv_output <- temp
  } else {
    wtv_output <- rbind(wtv_output, temp)
  }
}



```

```{r}
mycols <- colnames(wtv_output)
mycols[1] <-"wtv_ra"
mycols[2] <-"wtv_dec"
colnames(wtv_output) <-mycols
```

Append these results so we match back up with the epic

```{r}
k2_wtv <- cbind(k2_real_targets, wtv_output)
```

Double check that coordinates are the same for each row

```{r}
k2_wtv$check_col <- abs(k2_wtv$RA - k2_wtv$wtv_ra) + abs(k2_wtv$Dec - k2_wtv$wtv_dec)

jj <- which(k2_wtv$check_col > 1.5e-6) #not zero because we seem to get some round off
print(paste(length(jj), "rows have mis matched coordinates"))

```
So, let's move forward with this...

```{r}
k2_wtv$check_col <- NULL
```

Now let's just pull out the ones with TESS overlap...

```{r}
k2_wtv$num_sectors <- rowSums(k2_wtv[,9:47])

jj <- which(k2_wtv$num_sectors > 0)
print(paste("Number of entries with matches in wtv = ", length(jj)))

```

Let's just keep the ones with matches and ditch the rest

```{r}
k2_tess_overlaps <- k2_wtv %>% filter(num_sectors > 0)

```

Let's dump the duplicate coordinate columns and write this out for use in other notebooks.

```{r}
k2_tess_overlaps$wtv_ra <- NULL
k2_tess_overlaps$wtv_dec <- NULL

write_csv(k2_tess_overlaps,"overlaplists/all_k2_Sector1to39.csv")
```






